Relict deciduous oaks show high resilience to drought despite the effect of land-use legacies

### 2019-04-11 man/tables/t_dendro_summary.Rmd
tables

ta2 <- regulartable(t2, col_keys =c("name", "first_year", "last_year", "n_trees", "n_radii", "RW", "ms2",
                                   "ar1","rbar.wt","eps"))
ta2 <- ta2 %>% set_header_labels(name = "Site", first_year = "First year", last_year = "Last year",
                                 length_year = "Length (years)", n_trees ="# trees", n_radii = '# cores',
                                 RW ="RW (mm)", ms2="MS", ar1="AR(1)", rbar.wt = "Rbt", eps = "EPS") %>%
  align(align = "center", part = "header") %>% 
  bold(part = 'header') %>% 
  fontsize(part = "header", size = 10) %>% 
  fontsize(part = "body", size = 9) %>% 
  autofit(add_w = 0, add_h = 0) %>% 
  align(align = "center")

>>>>

ta2 <- regulartable(t2, col_keys =c("name", "first_year", "last_year", "length_year", "n_trees", "n_radii", "RW", "ms2",
                                   "ar1","rbar.wt","eps"))
ta2 <- ta2 %>% set_header_labels(name = "Site", first_year = "First year", last_year = "Last year",
                                 length_year = "Length (years)", n_trees ="# trees", n_radii = '# cores',
                                 RW ="RW (mm)", ms2="MS", ar1="AR(1)", rbar.wt = "Rbt", eps = "EPS") %>%
  align(align = "center", part = "header") %>% 
  bold(part = 'header') %>% 
  fontsize(part = "header", size = 10) %>% 
  fontsize(part = "body", size = 9) %>% 
  autofit(add_w = 0, add_h = 0) %>% 
  align(align = "center")
